---
title: "Statistical Analyses for Reputational Incentives Can Motivate Authentic Prosocial Signaling (Pilot Data)"
author: "Nathan Liang"
date: "April 25, 2023"
format: 
  html:
    code-fold: true
    code-tools: true
editor: "source"
number_sections: true
theme:
  dark: "darkly"
  light: "flatly"
---

# Import Packages and Datasets

## Identify Dependencies

```{r identify-dependencies, include=F, message=F, warning=F}
dependencies <- unique(renv::dependencies()$Package)
print(dependencies)
```

## Load Packages

```{r load-packages, include=F, message=F, warning=F}
if (!require(pacman)) install.packages('pacman'); require(pacman)

pacman::p_load(
  # Read/write data
  vroom, here, renv, janitor,
  
  # Reformat data
  dplyr, tidyr, tidyselect, stringr, forcats, knitr,
  lubridate, magrittr, rmarkdown, purrr,
  
  # Analyze data
  emmeans, effectsize, parameters, performance, rstatix, 
  car, scales, lmtest, psych,
  
  # Visualize data
  rlang, tune, sysfonts, ggplot2, ggrain, ggpp, ggtext, ggpattern, papaja)
```

## Read in Data

```{r read-raw-data, message=F, warning=F}
# Import raw data for pilot study
df_complete <- vroom::vroom(
  here::here("pilot/data/clean/pilot-data-clean-complete.csv"), 
  show_col_types = F, delim = ",") |> 
  dplyr::mutate(public_private = forcats::fct_relevel(public_private, c("public", "private")))
```

## Set Plotting Theme

```{r plotting-defaults, message=F, warning=F}
theme_nl <- function() {
  list(
    ggplot2::theme_bw() +
      ggplot2::theme(
        axis.ticks           = element_line(size = 0.25),
        axis.ticks.length    = unit(.05, units = "cm"),
        text                 = element_text(family = "Arial"),
        axis.title.x         = ggtext::element_markdown(size = 6, 
                                                        margin = margin(t = 5)),
        axis.text.x          = element_text(size = 5),
        axis.title.y         = ggtext::element_markdown(size = 6, angle = 90),
        axis.text.y          = element_text(size = 5),
        panel.grid.major     = element_line(size = 0.1, color = "darkgray"),
        panel.grid.minor     = element_line(size = 0.1, color = "darkgray"),
        panel.border         = element_blank(),  # Remove all borders
        axis.line.x          = element_line(color = "black", linewidth = 0.25),  # bottom border
        axis.line.y          = element_line(color = "black", linewidth = 0.25),  # left border
        strip.background     = element_rect(colour = "#D9D9D9"),
        strip.text           = element_text(size = 5, face = "bold"),
        legend.title         = ggtext::element_markdown(size = 6),
        legend.text          = element_text(size = 5),
        legend.key.size      = unit(.75, "line"),
        legend.justification = "center",
        legend.position      = "bottom",
        legend.box           = "horizontal"))
}
```

# Ensure Data Types are Correct

```{r demographics, message=F, warning=F}
# str(df)
df_complete <- df_complete |> 
  # Response ID
  dplyr::mutate(
    dplyr::across(c(
      batch, believe_real,
      unique_group_id, group_id, partner_choice, public_private), 
      as.factor)) |> 
  
  dplyr::mutate(
    
    # Race/Ethnicity
    ethnicity_simplified = factor(
      dplyr::case_match(
        ethnicity_simplified,
        "Mixed" ~ "Multiracial",
        .default = ethnicity_simplified)),
    
    # Sex
    sex = forcats::fct_relevel(factor(sex), "Male", "Female"),
    
    # Income
    income = forcats::fct_relevel(
      dplyr::case_match(
        income,
        "< $10,000"            ~ "<$10,000",
        "$10,000 to $19,999"   ~ "$10,000–$19,999",
        "$20,000 to $29,999"   ~ "$20,000–$29,999",
        "$30,000 to $39,999"   ~ "$30,000–$39,999",
        "$40,000 to $49,999"   ~ "$40,000–$49,999",
        "$50,000 to $74,999"   ~ "$50,000–$74,999",
        "$75,000 to $99,999"   ~ "$75,000–$99,999",
        "$100,000 to $149,999" ~ "$100,000–$149,999",
        .default = income),
      "<$10,000", 
      "$10,000–$19,999", 
      "$20,000–$29,999", 
      "$30,000–$39,999", 
      "$40,000–$49,999", 
      "$50,000–$74,999", 
      "$75,000–$99,999",
      "$100,000–$149,999", 
      ">$150,000"),
    
    # Education
    education = forcats::fct_relevel(
      dplyr::case_match(
        education,
        "Less than a high school diploma" ~ "< High school",
        "High school degree or equivalent (e.g. GED)" ~ "High school",
        "Associate Degree (e.g. AA, AS)"  ~ "Associate",
        "Some college, no degree" ~ "Some college, no degree",
        "Bachelor's Degree (e.g. BA, BS)" ~ "Bachelor's",
        paste(
          "Postgraduate Degree (e.g. Master's Degree,", 
          "Professional Degree, Doctorate Degree)"
        ) ~ "Postgraduate"
      ),
      "< High school",
      "High school",
      "Associate",
      "Some college, no degree",
      "Bachelor's",
      "Postgraduate"),
    
    # Employment Status
    employment_status = forcats::fct_relevel(
      dplyr::case_match(
        employment_status,
        paste(
          "Not in paid work (e.g. homemaker',",
          "'retired or disabled)") ~ "Other",
        "Unemployed (and job seeking)" ~ "Unemployed and not applying",
        .default = employment_status), 
      "Unemployed but applying", 
      "Part-Time", 
      "Full-Time", 
      "Other"),
    
    # Political Affiliation
    political_overall = forcats::fct_relevel(
      dplyr::case_match(
        political_overall,
        "Something else:" ~ "Other",
        .default = political_overall), 
      "Republican", "Democrat", "Independent", "Other"),
    believe_real = dplyr::if_else(believe_real == "Yes", 1, 0))
```

------------------------------------------------------------------------
# Descriptives

## Demographics

::: {.panel-tabset .nav-pills}
### Race/Ethnicity and Gender

```{r demographics-race-ethnicity-gender, message=F, warning=F, echo=F}
# ---------------------- #
# DESCRIPTIVE STATISTICS #
# ---------------------- #
# Race/Ethnicity
df_complete |> 
  dplyr::select(ethnicity_simplified) |>
  dplyr::summarize(
    percent_total = dplyr::n() / nrow(df_complete) * 100, 
    .by = ethnicity_simplified) |> 
  # dplyr::ungroup() |>
  dplyr::arrange(ethnicity_simplified, desc(percent_total)) |> 
  knitr::kable(
    col.names = c("Race/Ethnicity", "Percent"),
    digits = c(0, 2))

# Sex
df_complete |> 
  dplyr::select(sex) |>
  dplyr::summarize(
    percent_total = dplyr::n() / nrow(df_complete) * 100, 
    .by = sex) |> 
  dplyr::arrange(sex, desc(percent_total)) |> 
  knitr::kable(
    col.names = c("Sex", "Percent"),
    digits = c(0, 2))

# Age
df_complete |> 
  dplyr::select(age) |> 
  rstatix::get_summary_stats() |> 
  knitr::kable(
    col.names = c(
      "Variable", "n", "Min", "Max", "Median", "Q1", "Q3", "IQR", 
      "MAD", "Mean", "SD", "SE", "95% CI"),
    digits = c(0, 0, 0, 0, 0, 0, 0, 0, 2, 2, 2, 2, 2))

# -------- #
# DATA VIS #
# -------- #
# Race/Ethnicity and Sex
df_complete |> 
  dplyr::select(ethnicity_simplified, sex) |> 
  tidyr::drop_na() |>
  ggplot2::ggplot(
    ggplot2::aes(
      x    = ethnicity_simplified, 
      fill = sex)) + 
  ggplot2::geom_bar(position = position_dodge()) +
  ggplot2::labs(
    title = "Race/Ethnicity by Sex Distribution",
    x     = "Race/Ethnicity",
    y     = "Count",
    fill  = "Sex") +
  ggplot2::scale_fill_manual(values = c("#00A9FF", "#ED68ED", "#8494FF")) +
  theme_nl()

# Age
df_complete |> 
  dplyr::select(age) |> 
  ggplot2::ggplot(ggplot2::aes(x = age)) + 
  ggplot2::geom_bar() +
  ggplot2::labs(
    title = "Age Distribution",
    x     = "Age",
    y     = "Count") + 
  theme_nl()

# Income
df_complete |> 
  dplyr::select(income) |> 
  tidyr::drop_na() |>
  ggplot2::ggplot(ggplot2::aes(x = income)) + 
  ggplot2::geom_bar() +
  ggplot2::labs(
    title = "Income Distribution",
    x     = "Income",
    y     = "Count") + 
  ggplot2::theme(axis.text.x = ggplot2::element_text(angle = 45)) +
  theme_nl()

# Education
df_complete |> 
  dplyr::select(education) |> 
  tidyr::drop_na() |>
  ggplot2::ggplot(
    ggplot2::aes(x = education)) + 
  ggplot2::geom_bar() +
  ggplot2::labs(
    title = "Education Distribution",
    x     = "Education",
    y     = "Count") + 
  theme_nl() +
  ggplot2::theme(axis.text.x = ggplot2::element_text(angle = 45))

# Employment Status
df_complete |> 
  dplyr::select(employment_status) |> 
  tidyr::drop_na() |>
  ggplot2::ggplot(ggplot2::aes(x = employment_status)) + 
  ggplot2::geom_bar() +
  ggplot2::labs(
    title = "Employment Status Distribution",
    x     = "Employment Status",
    y     = "Count") + 
  theme_nl() +
  ggplot2::theme(axis.text.x = ggplot2::element_text(angle = 45))

# Political Affiliation
df_complete |> 
  dplyr::select(political_overall) |> 
  tidyr::drop_na() |>
  ggplot2::ggplot(
    ggplot2::aes(
      x    = political_overall,
      fill = political_overall)) + 
  ggplot2::geom_bar() +
  ggplot2::labs(
    title = "Political Affiliation Distribution",
    x     = "Political Affiliation",
    y     = "Count") + 
  ggplot2::guides(fill = "none") +
  ggplot2::scale_fill_manual(values = c("#F8766D", "#35A2FF", "#8494FF", "#39B600"))
  theme_nl()
```
:::

------------------------------------------------------------------------

# Supplementary Information

## Preregistered Analyses

### Preregistered H1 (H1 in Main Paper)

Independent-Samples T-Test

```{r hypothesis-1-prereg-t-test, message=F, warning=F}
# --------- #
# PREP DATA #
# --------- #
df_pre1 <- df_complete |> 
  dplyr::select(
    participant_role, public_private, partner_choice, dg_a_gen_transfer) |> 
  dplyr::filter(stringr::str_starts(participant_role, "A")) |> 
  tidyr::drop_na(dg_a_gen_transfer) |> 
  dplyr::mutate(public_private = forcats::fct_relevel(public_private, "public"))

# -------------------------- #
# INDEPENDENT-SAMPLES T-TEST #
# -------------------------- #
ttest_pre1 <- t.test(
  formula     = dg_a_gen_transfer ~ public_private, 
  data        = df_pre1, 
  alternative = "greater")
parameters::model_parameters(ttest_pre1)
effectsize::effectsize(ttest_pre1)

# ------------ #
# LINEAR MODEL #
# ------------ #
lm_pre1 <- lm(
  formula   = dg_a_gen_transfer ~ public_private, 
  data      = df_pre1, 
  contrasts = list(public_private = "contr.sum"))

# ------------------------ #
# ESTIMATED MARGINAL MEANS #
# ------------------------ #
# table(df_preh1$public_private)
# Observability: Public - Private
parameters::model_parameters(
  emmeans::emmeans(lm_pre1, specs = ~public_private))
```

### Preregistered H2 (H4 in Main Paper)

Linear Regression

Comparing initial trustor generosity in the TG by observability controlling for
generosity in the DG.

```{r hypothesis-4-prereg-lm, message=F, warning=F}
# --------- #
# PREP DATA #
# --------- #
df_pre2 <- df_complete |>
  dplyr::filter(!stringr::str_starts(participant_role, "B")) |>
  dplyr::select(
    unique_group_id, participant_role, 
    public_private, partner_choice,
    dg_a_chosen_transfer_ratio, tg_c_transfer_ratio) |> 
  dplyr::group_by(unique_group_id) |> 
  dplyr::mutate(
    dg_a_chosen_transfer_ratio = dplyr::if_else(
      is.na(dg_a_chosen_transfer_ratio), 
      dplyr::first(na.omit(dg_a_chosen_transfer_ratio)), 
      dg_a_chosen_transfer_ratio),
    tg_c_transfer_ratio = dplyr::if_else(
      is.na(tg_c_transfer_ratio), 
      dplyr::first(na.omit(tg_c_transfer_ratio)), 
      tg_c_transfer_ratio)) |> 
  dplyr::ungroup() |>
  dplyr::distinct(unique_group_id, .keep_all = T) |> 
  dplyr::arrange(unique_group_id, participant_role)

# ------------ #
# LINEAR MODEL #
# ------------ #
lm_pre2 <- lm(
  formula   = tg_c_transfer_ratio ~ public_private + dg_a_chosen_transfer_ratio, 
  data      = df_pre2, 
  contrasts = list(public_private = "contr.sum"))

# -------------- #
# TYPE III ANOVA #
# -------------- #
anova_lm_pre2 <- car::Anova(lm_pre2, type = 3)
parameters::model_parameters(lm_pre2)
effectsize::effectsize(lm_pre2)

# ------------ #
# LINEAR MODEL #
# ------------ #
# As an additional test, do not control for DG generosity
lm_pre2 <- lm(
  formula   = tg_c_transfer_ratio ~ public_private, 
  data      = df_pre2, 
  contrasts = list(public_private = "contr.sum"))

# ------------------------ #
# ESTIMATED MARGINAL MEANS #
# ------------------------ #
# table(df_pre4$public_private)
lm_pre2_obs_emm <- emmeans::emmeans(lm_pre2, specs = ~public_private)
parameters::model_parameters(lm_pre2_obs_emm)

# -------------------- #
# PAIRWISE COMPARISONS #
# -------------------- #
# Observability: Public - Private
parameters::model_parameters(
  emmeans::contrast(
    object = lm_pre2_obs_emm, 
    method = "pairwise", 
    infer  = T, 
    adj    = "none"))
```

### Preregistered H3 (Not in Main Text)

Linear Regression

```{r hypothesis-3-prereg-lm, message=F, warning=F}
# --------- #
# PREP DATA #
# --------- #
df_pre3 <- df_complete |>
  dplyr::filter((participant_role == "C") & (partner_choice == "yes")) |> 
  dplyr::select(
    participant_role, tg_partner_choice, dg_a1_transfer_ratio, dg_a2_transfer_ratio, tg_partner_choice) |> 
  dplyr::mutate(
    dg_transfer_ratio_diff = dg_a1_transfer_ratio - dg_a2_transfer_ratio)

# ------------ #
# LINEAR MODEL #
# ------------ #
lm_pre3 <- lm(
  formula    = dg_transfer_ratio_diff ~ tg_partner_choice, 
  data       = df_pre3, 
  contrasts  = list(tg_partner_choice = "contr.sum"))

# ------------------------ #
# ESTIMATED MARGINAL MEANS #
# ------------------------ #
# table(df_pre3$tg_partner_choice)
lm_pre3_tg_pc_emm <- emmeans::emmeans(lm_pre3, specs = ~tg_partner_choice)
parameters::model_parameters(lm_pre3_tg_pc_emm)

# -------------------- #
# PAIRWISE COMPARISONS #
# -------------------- #
# Partner Choice: A1 - A2
parameters::model_parameters(
  emmeans::contrast(
    object = lm_pre3_tg_pc_emm, 
    method = "pairwise", 
    infer  = T, 
    adj    = "none"))

# ------------------------------- #
# EFFECT SIZE FOR MEAN COMPARISON #
# ------------------------------- #
# Partner Choice: A1 - A2 (Cohen's d)
parameters::model_parameters(
  emmeans::eff_size(
    object = lm_pre3_tg_pc_emm, 
    sigma  = sigma(lm_pre3), 
    edf    = df.residual(lm_pre3)))
```

### Preregistered H4 (H3 in Main Paper)

Linear Regression

@h3-prereg-lm
@h3-morality-lm

### Preregistered H5 (H2 in Main Paper)

Linear Regression

The transfer difference is more negative (A2 gave more than A1) when A2 is 
picked -- in other words, A2 is picked when they give more than A1.

```{r hypothesis-5-prereg-lm, message=F, warning=F}
# --------- #
# PREP DATA #
# --------- #
df_pre5 <- df_complete |> 
  dplyr::filter(!stringr::str_starts(participant_role, "B")) |>
  dplyr::select(
    unique_group_id, participant_role, public_private, partner_choice,
    dg_a_chosen_transfer_ratio, tg_a_return_ratio) |> 
  dplyr::group_by(unique_group_id) |> 
  dplyr::mutate(
    dg_a_chosen_transfer_ratio = dplyr::if_else(
      is.na(dg_a_chosen_transfer_ratio), 
      dplyr::first(na.omit(dg_a_chosen_transfer_ratio)), 
      dg_a_chosen_transfer_ratio),
    tg_a_return_ratio = dplyr::if_else(
      is.na(tg_a_return_ratio),
      dplyr::first(na.omit(tg_a_return_ratio)), 
      tg_a_return_ratio)) |> 
  dplyr::ungroup() |>
  dplyr::arrange(unique_group_id, participant_role) |> 
  dplyr::distinct(unique_group_id, .keep_all = T)

# ------------ #
# LINEAR MODEL #
# ------------ #
lm_pre5 <- lm(
  formula = tg_a_return_ratio ~ dg_a_chosen_transfer_ratio, 
  data    = df_pre5)

parameters::model_parameters(lm_pre5)
```

--------------------------------------------------------------------------------

# Main Text Analyses

## H1: "Expressed as Signal"

### Modeling Game Behavior

```{r hypothesis-1-behavioral-lm, message=F, warning=F}
# --------- #
# PREP DATA #
# --------- #
df_h1 <- df_complete |> 
  dplyr::select(
    participant_role, public_private, partner_choice, dg_a_gen_transfer_ratio) |> 
  dplyr::filter(stringr::str_starts(participant_role, "A")) |> 
  tidyr::drop_na(dg_a_gen_transfer_ratio) |> 
  dplyr::mutate(
    partner_choice = forcats::fct_relevel(
      dplyr::case_when(
        partner_choice == "yes" ~ "Yes",
        partner_choice == "no"  ~ "No"),
      c("No", "Yes")),
    public_private = forcats::fct_relevel(
      dplyr::case_when(
        public_private == "public"  ~ "Public",
        public_private == "private" ~ "Private"),
      c("Private", "Public")))
```

#### Linear Model

```{r hypothesis-1-lm, message=F, warning=F}
# ------------ #
# LINEAR MODEL #
# ------------ #
lm_h1 <- lm(
  formula   = dg_a_gen_transfer_ratio ~ public_private + partner_choice, 
  data      = df_h1,
  contrasts = list(
    public_private = "contr.sum", 
    partner_choice = "contr.sum"))

# -------------- #
# TYPE III ANOVA #
# -------------- #
anova_lm_h1 <- car::Anova(lm_h1, type = 3)
parameters::model_parameters(anova_lm_h1)
effectsize::effectsize(anova_lm_h1)

# ------------------------ #
# ESTIMATED MARGINAL MEANS #
# ------------------------ #
# table(df_h1$public_private)
lm_h1_obs_emm <- emmeans::emmeans(lm_h1, specs = ~public_private)
parameters::model_parameters(lm_h1_obs_emm)

# table(df_h1$partner_choice)
lm_h1_pc_emm  <- emmeans::emmeans(lm_h1, specs = ~partner_choice)
parameters::model_parameters(lm_h1_pc_emm)

# -------------------- #
# PAIRWISE COMPARISONS #
# -------------------- #
# Observability: Public - Private
parameters::model_parameters(
  emmeans::contrast(
    object = lm_h1_obs_emm, 
    method = "pairwise",
    infer  = T, 
    adjust = "none"))

# Partner Choice: Yes - No
parameters::model_parameters(
  emmeans::contrast(
    object = lm_h1_pc_emm, 
    method = "pairwise", 
    infer  = T, 
    adjust = "none"))

# --------------------------------- #
# EFFECT SIZES FOR MEAN COMPARISONS #
# --------------------------------- #
# Observability: Public - Private (Cohen's d)
parameters::model_parameters(
  emmeans::eff_size(
    object = lm_h1_obs_emm, 
    sigma  = sigma(lm_h1), 
    edf    = df.residual(lm_h1)))

# Partner Choice: Yes - No (Cohen's d)
parameters::model_parameters(
  emmeans::eff_size(
    object = lm_h1_pc_emm, 
    sigma  = sigma(lm_h1), 
    edf    = df.residual(lm_h1)))
```

------------------------------------------------------------------------

## H2: Actually a Signal

### Modeling Game Behavior

```{r hypothesis-2-prep-data, message=F, warning=F}
# --------- #
# PREP DATA #
# --------- #
df_h2 <- df_pre5
```

#### Linear Model

```{r hypothesis-2-lm, message=F, warning=F}
# ------------ #
# LINEAR MODEL #
# ------------ #
lm_h2 <- lm(
  formula   = tg_a_return_ratio ~ public_private + partner_choice + dg_a_chosen_transfer_ratio, 
  data      = df_h2,
  contrasts = list(
    public_private = "contr.sum",
    partner_choice = "contr.sum"))

# -------------- #
# TYPE III ANOVA #
# -------------- #
anova_lm_h2 <- car::Anova(lm_h2, type = 3)
parameters::model_parameters(anova_lm_h2)
effectsize::effectsize(anova_lm_h2)

# ---------------------- #
# AVERAGE MARGINAL TREND #
# ---------------------- #
parameters::model_parameters(
  emmeans::emtrends(lm_h2, ~1, var = "dg_a_chosen_transfer_ratio", infer = T))

# ------------------------ #
# ESTIMATED MARGINAL MEANS #
# ------------------------ #
# table(df_h2$public_private)
# Observability: Public - Private
lm_h2_obs_emm <- emmeans::emmeans(lm_h2, specs = ~public_private)
parameters::model_parameters(lm_h2_obs_emm)

# table(df_h2$partner_choice)
# Partner Choice: Yes - No
lm_h2_pc_emm  <- emmeans::emmeans(lm_h2, specs = ~partner_choice)
parameters::model_parameters(lm_h2_pc_emm)

# -------------------- #
# PAIRWISE COMPARISONS #
# -------------------- #
# Observability: Public - Private
parameters::model_parameters(
  emmeans::contrast(
    object = lm_h2_obs_emm, 
    method = "pairwise", 
    infer  = T, 
    adjust = "none"))

# Partner Choice: Yes - No
parameters::model_parameters(
  emmeans::contrast(
    object = lm_h2_pc_emm,  
    method = "pairwise", 
    infer  = T, 
    adjust = "none"))

# --------------------------------- #
# EFFECT SIZES FOR MEAN COMPARISONS #
# --------------------------------- #
# Observability: Public - Private (Cohen's d)
parameters::model_parameters(
  emmeans::eff_size(
    object = lm_h2_obs_emm, 
    sigma  = sigma(lm_h2), 
    edf    = df.residual(lm_h2)))

# Partner Choice: Yes - No (Cohen's d)
parameters::model_parameters(
  emmeans::eff_size(
    object = lm_h2_pc_emm, 
    sigma  = sigma(lm_h2), 
    edf    = df.residual(lm_h2)))
```

#### Curvilinear Model

```{r hypothesis-2-qm, message=F, warning=F}
# --------------- #
# QUADRATIC MODEL #
# --------------- #
qm_h2 <- lm(
  formula   = tg_a_return_ratio ~ public_private + partner_choice + dg_a_chosen_transfer_ratio + I(dg_a_chosen_transfer_ratio^2), 
  data      = tidyr::drop_na(df_h2, dg_a_chosen_transfer_ratio),
  contrasts = list(
    public_private = "contr.sum", 
    partner_choice = "contr.sum"))

# ---------------------- #
# AVERAGE MARGINAL TREND #
# ---------------------- #
parameters::model_parameters(
  emmeans::emtrends(
    qm_h2, ~1, var = "dg_a_chosen_transfer_ratio", infer = T, max.degree = 2))

# -------------- #
# TYPE III ANOVA #
# -------------- #
anova_qm_h2 <- car::Anova(qm_h2, type = 3)
parameters::model_parameters(anova_qm_h2)
effectsize::effectsize(anova_qm_h2)

# ------------------------ #
# ESTIMATED MARGINAL MEANS #
# ------------------------ #
# table(df_h2$public_private)
# Observability: Public - Private
qm_h2_obs_emm <- emmeans::emmeans(qm_h2, specs = ~public_private)
parameters::model_parameters(qm_h2_obs_emm)

# table(df_h2$partner_choice)
# Partner Choice: Yes - No
qm_h2_pc_emm  <- emmeans::emmeans(qm_h2, specs = ~partner_choice)
parameters::model_parameters(qm_h2_pc_emm)

# -------------------- #
# PAIRWISE COMPARISONS #
# -------------------- #
# Observability: Public - Private
parameters::model_parameters(
  emmeans::contrast(
    object = qm_h2_obs_emm, 
    method = "pairwise", 
    infer  = T, 
    adjust = "none"))

# Partner Choice: Yes - No
parameters::model_parameters(
  emmeans::contrast(
    object = qm_h2_pc_emm,  
    method = "pairwise", 
    infer  = T, 
    adjust = "none"))

# --------------------------------- #
# EFFECT SIZES FOR MEAN COMPARISONS #
# --------------------------------- #
# Observability: Public - Private (Cohen's d)
parameters::model_parameters(
  emmeans::eff_size(
    object = qm_h2_obs_emm, 
    sigma  = sigma(qm_h2), 
    edf    = df.residual(qm_h2)))

# Partner Choice: Yes - No (Cohen's d)
parameters::model_parameters(
  emmeans::eff_size(
    object = qm_h2_pc_emm, 
    sigma  = sigma(qm_h2), 
    edf    = df.residual(qm_h2)))
```

------------------------------------------------------------------------

## H3: Perceived as Signal

### Modeling Game Behavior

```{r hypothesis-3-lm, message=F, warning=F}
# --------- #
# PREP DATA #
# --------- #
df_h3a <- df_complete |>
  dplyr::filter(!stringr::str_starts(participant_role, "B")) |>
  dplyr::select(
    unique_group_id, participant_role, public_private, partner_choice,
    dg_a_chosen_transfer_ratio, tg_c_transfer_ratio) |> 
  dplyr::group_by(unique_group_id) |> 
  dplyr::mutate(
    dg_a_chosen_transfer_ratio = dplyr::if_else(
      is.na(dg_a_chosen_transfer_ratio), 
      dplyr::first(na.omit(dg_a_chosen_transfer_ratio)), 
      dg_a_chosen_transfer_ratio),
    tg_c_transfer_ratio = dplyr::if_else(
      is.na(tg_c_transfer_ratio),
      dplyr::first(na.omit(tg_c_transfer_ratio)), 
      tg_c_transfer_ratio)) |> 
  dplyr::ungroup() |>
  dplyr::arrange(unique_group_id, participant_role) |> 
  dplyr::distinct(unique_group_id, .keep_all = T)
```

#### Linear Model

```{r hypothesis-3-behavioral-lm, message=F, warning=F}
# ------------ #
# LINEAR MODEL #
# ------------ #
lm_h3a <- lm(
  formula = tg_c_transfer_ratio ~ dg_a_chosen_transfer_ratio, 
  data    = df_h3a)

# Unstandardized Regression Coefficient
parameters::model_parameters(lm_h3a)

# Standardized Regression Coefficient
effectsize::effectsize(lm_h3a)
```

#### Curvilinear Model

```{r hypothesis-3-behavioral-qm, message=F, warning=F}
# --------------- #
# QUADRATIC MODEL #
# --------------- #
qm_h3a <- lm(
  formula = tg_c_transfer_ratio ~ dg_a_chosen_transfer_ratio + I(dg_a_chosen_transfer_ratio^2), 
  data    = df_h3a)

# ----------------------- #
# AVERAGE MARGINAL TREND # 
# ----------------------- #
parameters::model_parameters(
  emmeans::emtrends(qm_h3a, ~1, var = "dg_a_chosen_transfer_ratio", max.degree = 2))

# -------------------------------------- #
# UNSTANDARDIZED REGRESSION COEFFICIENTS #
# -------------------------------------- #
parameters::model_parameters(qm_h3a)

# ------------------------------------ #
# STANDARDIZED REGRESSION COEFFICIENTS #
# ------------------------------------ #
effectsize::effectsize(qm_h3a)
```

### Modeling Morality Ratings

```{r hypothesis-3b-prep-data, message=F, warning=F}
# --------- #
# PREP DATA #
# --------- #
df_h3b <- df_complete |> 
  ## Select relevant columns
  dplyr::select(
    participant_id, unique_group_id, participant_role, 
    public_private, partner_choice,
    
    ### DG A/A1/A2 transfers and morality ratings
    dg_a_transfer_ratio, dg_a1_transfer_ratio, dg_a2_transfer_ratio, 
    dg_a_moral, dg_a1_moral, dg_a2_moral) |> 
  
  ## Pivot morality ratings 
  ### dg_a_moral | dg_a1_moral | ... | swing into one column
  tidyr::pivot_longer(
    !c(participant_id, unique_group_id, participant_role, 
       public_private, partner_choice,
       dg_a_transfer_ratio, dg_a1_transfer_ratio, dg_a2_transfer_ratio), 
    names_to = "morality_target", values_to = "morality_rating") |> 
  tidyr::drop_na(morality_rating) |> 
  
  ## Pivot transfer allocation ratios
  ### dg_a_transfer_ratio | dg_a1_transfer_ratio | ... | swing into one column
  tidyr::pivot_longer(
    !c(participant_id, unique_group_id, participant_role, 
       public_private, partner_choice, morality_target, morality_rating), 
    names_to = "transfer_allocator", values_to = "transfer_ratio") |> 
  tidyr::drop_na(transfer_ratio) |>
  
  ## Only keep morality ratings / transfers corresponding to same target / game stage
  dplyr::filter(
    (stringr::str_starts(morality_target, "dg_a_") & 
       stringr::str_starts(transfer_allocator, "dg_a_")) |
      (stringr::str_starts(morality_target, "dg_a1_") & 
         stringr::str_starts(transfer_allocator, "dg_a1_")) |
      (stringr::str_starts(morality_target, "dg_a2_") & 
         stringr::str_starts(transfer_allocator, "dg_a2_"))) |>
  
  ## Remove "_moral" suffix from each morality rating target, make rest uppercase
  dplyr::mutate(
    morality_target = stringr::str_sub(stringr::str_to_upper(
      stringr::str_remove(morality_target, "moral")), end = -2)) |> 
  
  ## Distinguish game (DG vs. TG)---even though it's just DG
  tidyr::separate_wider_delim(
    morality_target, delim = "_", 
    names = c("morality_target_game", "morality_target")) |> 
  dplyr::mutate(
    transfer_allocator = stringr::str_remove(transfer_allocator, "_ratio")) |> 
  dplyr::select(-morality_target_game) |> 
  
  ## Code self-other
  dplyr::mutate(
    self_other = dplyr::if_else(participant_role == morality_target, "self", "other"),
    .before = public_private)
```

#### Linear Model

```{r hypothesis-3b-lm, message=F, warning=F}
# ------------ #
# LINEAR MODEL #
# ------------ #
lm_h3b <- lm(
  formula   = morality_rating ~ participant_role + transfer_ratio, 
  data      = dplyr::filter(df_h3b, self_other == "other"),
  contrasts = list(participant_role = "contr.sum"))

# -------------- #
# TYPE III ANOVA #
# -------------- #
anova_lm_h3b <- car::Anova(lm_h3b, type = 3)
parameters::model_parameters(anova_lm_h3b)
effectsize::effectsize(anova_lm_h3b)

# ------------------------ #
# ESTIMATED MARGINAL MEANS #
# ------------------------ #
table(dplyr::filter(df_h3b, self_other == "other")$participant_role)
lm_h3b_role_emm <- emmeans::emmeans(lm_h3b, specs = ~participant_role)
parameters::model_parameters(lm_h3b_role_emm)

# -------------------- #
# PAIRWISE COMPARISONS #
# -------------------- #
# Participant Role: B - C
parameters::model_parameters(
  emmeans::contrast(
    object = lm_h3b_role_emm, 
    method = "pairwise", 
    infer  = T, 
    adjust = "none"))

# ------------------------------- #
# EFFECT SIZE FOR MEAN COMPARISON #
# ------------------------------- #
# Participant Role: B - C (Cohen's d)
parameters::model_parameters(
  emmeans::eff_size(
    object = lm_h3b_role_emm, 
    sigma  = sigma(lm_h3b), 
    edf    = df.residual(lm_h3b)))
```

#### Curvilinear Model

```{r hypothesis-3b-qm, message=F, warning=F}
# --------------- #
# QUADRATIC MODEL #
# --------------- #
qm_h3b <- lm(
  formula   = morality_rating ~ participant_role + transfer_ratio + I(transfer_ratio^2), 
  data      = dplyr::filter(df_h3b, self_other == "other"),
  contrasts = list(participant_role = "contr.sum"))

# -------------- #
# TYPE III ANOVA #
# -------------- #
anova_qm_h3b <- car::Anova(qm_h3b, type = 3)
parameters::model_parameters(anova_qm_h3b)
effectsize::effectsize(anova_qm_h3b)

# ---------------------- #
# AVERAGE MARGINAL TREND #
# ---------------------- #
parameters::model_parameters(
  emmeans::emtrends(qm_h3b, ~1, var = "transfer_ratio", max.degree = 2))

# ------------------------ #
# ESTIMATED MARGINAL MEANS #
# ------------------------ #
# table(dplyr::filter(df_h3b, self_other == "other")$participant_role)
qm_h3b_role_emm <- emmeans::emmeans(qm_h3b, specs = ~participant_role) 
parameters::model_parameters(qm_h3b_role_emm)

# -------------------- #
# PAIRWISE COMPARISONS #
# -------------------- #
# Participant Role: B - C
parameters::model_parameters(
  emmeans::contrast(
    object = qm_h3b_role_emm, 
    method = "pairwise", 
    infer  = T, 
    adjust = "none"))

# ------------------------------- #
# EFFECT SIZE FOR MEAN COMPARISON #
# ------------------------------- #
# Participant Role: B - C (Cohen's d)
parameters::model_parameters(
  emmeans::eff_size(
    object = qm_h3b_role_emm, 
    sigma  = sigma(qm_h3b), 
    edf    = df.residual(qm_h3b)))
```

------------------------------------------------------------------------

## H4: "Discounted as Signal"

### Modeling Game Behavior

```{r hypothesis-4a-prep-data, message=F, warning=F}
# --------- #
# PREP DATA #
# --------- #
df_h4a <- df_pre2
```

#### Linear Model

```{r hypothesis-4a-lm, message=F, warning=F}
# ------------ #
# LINEAR MODEL #
# ------------ #
lm_h4a <- lm(
  formula   = tg_c_transfer_ratio ~ public_private + partner_choice + dg_a_chosen_transfer_ratio,
  data      = df_h4a,
  contrasts = list(
    public_private = "contr.sum", 
    partner_choice = "contr.sum"))

# -------------- #
# TYPE III ANOVA #
# -------------- #
anova_lm_h4a <- car::Anova(lm_h4a, type = 3)
parameters::model_parameters(anova_lm_h4a)
effectsize::effectsize(anova_lm_h4a)

# ------------------------ #
# ESTIMATED MARGINAL MEANS #
# ------------------------ #
# table(df_h4a$public_private)
lm_h4a_obs_emm <- emmeans::emmeans(lm_h4a, specs = ~public_private)
parameters::model_parameters(lm_h4a_obs_emm)

# table(df_h4a$partner_choice)
lm_h4a_pc_emm  <- emmeans::emmeans(lm_h4a, specs = ~partner_choice)
parameters::model_parameters(lm_h4a_pc_emm)

# -------------------- #
# PAIRWISE COMPARISONS #
# -------------------- #
# Observability: Public - Private
parameters::model_parameters(
  emmeans::contrast(
    object = lm_h4a_obs_emm, 
    method = "pairwise",
    infer  = T, 
    adjust = "none"))

# Partner Choice: Yes - No
parameters::model_parameters(
  emmeans::contrast(
    object = lm_h4a_pc_emm, 
    method = "pairwise", 
    infer  = T, 
    adjust = "none"))

# --------------------------------- #
# EFFECT SIZES FOR MEAN COMPARISONS #
# --------------------------------- #
# Observability: Public - Private (Cohen's d)
parameters::model_parameters(
  emmeans::eff_size(
    object = lm_h4a_obs_emm, 
    sigma  = sigma(lm_h4a), 
    edf    = df.residual(lm_h4a)))

# Partner Choice: Yes - No (Cohen's d)
parameters::model_parameters(
  emmeans::eff_size(
    object = lm_h4a_pc_emm, 
    sigma  = sigma(lm_h4a), 
    edf    = df.residual(lm_h4a)))
```

#### Curvilinear Model

```{r hypothesis-4a-qm, message=F, warning=F}
# --------------- #
# QUADRATIC MODEL #
# --------------- #
qm_h4a <- lm(  # subsetting on "other"
  formula   = tg_c_transfer_ratio ~ public_private + partner_choice + dg_a_chosen_transfer_ratio + I(dg_a_chosen_transfer_ratio^2), 
  data      = df_h4a,
  contrasts = list(
    public_private = "contr.sum", 
    partner_choice = "contr.sum"))  

# ---------------------- #
# AVERAGE MARGINAL TREND #
# ---------------------- #
parameters::model_parameters(
  emmeans::emtrends(qm_h4a, ~1, var = "dg_a_chosen_transfer_ratio", max.degree = 2))

# -------------- #
# TYPE III ANOVA #
# -------------- #
anova_qm_h4a <- car::Anova(qm_h4a, type = 3)
parameters::model_parameters(anova_qm_h4a)
effectsize::effectsize(anova_qm_h4a)

# ------------------------ #
# ESTIMATED MARGINAL MEANS #
# ------------------------ #
# table(df_h4a$public_private)
# Observability: Public - Private
qm_h4a_obs_emm <- emmeans::emmeans(qm_h4a, specs = ~public_private) 
parameters::model_parameters(qm_h4a_obs_emm)

# Partner Choice: Yes - No
qm_h4a_pc_emm  <- emmeans::emmeans(qm_h4a, specs = ~partner_choice)
parameters::model_parameters(qm_h4a_pc_emm)

# -------------------- #
# PAIRWISE COMPARISONS #
# -------------------- #
# Observability: Public - Private
parameters::model_parameters(
  emmeans::contrast(
    object = qm_h4a_obs_emm, 
    method = "pairwise", 
    infer  = T, 
    adjust = "none"))

# Partner Choice: Yes - No
parameters::model_parameters(
  emmeans::contrast(
    object = qm_h4a_pc_emm, 
    method = "pairwise", 
    infer  = T, 
    adjust = "none"))

# --------------------------------- #
# EFFECT SIZES FOR MEAN COMPARISONS #
# --------------------------------- #
# Observability: Public - Private (Cohen's d)
parameters::model_parameters(
  emmeans::eff_size(
    object = qm_h4a_obs_emm, 
    sigma  = sigma(qm_h4a), 
    edf    = df.residual(qm_h4a)))

# Partner Choice: Yes - No (Cohen's d)
parameters::model_parameters(
  emmeans::eff_size(
    object = qm_h4a_pc_emm, 
    sigma  = sigma(qm_h4a), 
    edf    = df.residual(qm_h4a)))
```

### Modeling Morality Ratings

```{r hypothesis-4b-prep-data, message=F, warning=F}
# --------- #
# PREP DATA #
# --------- #
df_h4b <- df_h3b
```

#### Linear Model

```{r hypothesis-4b-lm, message=F, warning=F}
# ------------ #
# LINEAR MODEL #
# ------------ #
lm_h4b <- lm(  # subsetting on "other"
  formula   = morality_rating ~ public_private * partner_choice + transfer_ratio, 
  data      = dplyr::filter(df_h4b, self_other == "other"), 
  contrasts = list(
    partner_choice = "contr.sum", 
    public_private = "contr.sum"))

# -------------- #
# TYPE III ANOVA #
# -------------- #
anova_h4b <- car::Anova(lm_h4b, type = 3)
parameters::model_parameters(anova_h4b)
effectsize::effectsize(anova_h4b)

# ------------------------ #
# ESTIMATED MARGINAL MEANS #
# ------------------------ #
# table(dplyr::filter(df_h4b, self_other == "other")$public_private)
# Observability: Public - Private
lm_h4b_obs_emm <- emmeans::emmeans(lm_h4b, specs = ~public_private) 
parameters::model_parameters(lm_h4b_obs_emm)

# table(dplyr::filter(df_h4b, self_other == "other")$partner_choice)
# Partner Choice: No - Yes
lm_h4b_pc_emm  <- emmeans::emmeans(lm_h4b, specs = ~partner_choice) 
parameters::model_parameters(lm_h4b_pc_emm)

# -------------------- #
# PAIRWISE COMPARISONS #
# -------------------- #
# Observability: Public - Private
parameters::model_parameters(
  emmeans::contrast(
    object = lm_h4b_obs_emm, 
    method = "pairwise", 
    infer  = T, 
    adjust = "none"))

# Partner Choice: No - Yes
parameters::model_parameters(
  emmeans::contrast(
    object = lm_h4b_pc_emm, 
    method = "pairwise",
    infer  = T, 
    adjust = "none"))

# --------------------------------- #
# EFFECT SIZES FOR MEAN COMPARISONS #
# --------------------------------- #
# Observability: Public - Private (Cohen's d)
parameters::model_parameters(
  emmeans::eff_size(
    object = lm_h4b_obs_emm, 
    sigma  = sigma(lm_h4b), 
    edf    = df.residual(lm_h4b)))

# Partner Choice: No - Yes (Cohen's d)
parameters::model_parameters(
  emmeans::eff_size(
    object = lm_h4b_pc_emm, 
    sigma  = sigma(lm_h4b), 
    edf    = df.residual(lm_h4b)))
```

#### Curvilinear Model

```{r hypothesis-4b-qm, message=F, warning=F}
# --------------- #
# QUADRATIC MODEL #
# --------------- #
qm_h4b <- lm(  # subsetting on "other"
  formula   = morality_rating ~ public_private * partner_choice + transfer_ratio + I(transfer_ratio^2), 
  data      = dplyr::filter(df_h4b, self_other == "other"),
  contrasts = list(
    partner_choice = "contr.sum", 
    public_private = "contr.sum"))

# -------------- #
# TYPE III ANOVA #
# -------------- #
anova_qm_h4b <- car::Anova(qm_h4b, type = 3)
parameters::model_parameters(anova_qm_h4b)
effectsize::effectsize(anova_qm_h4b)

# ---------------------- #
# INTERACTION DECOMPOSED #
# ---------------------- #
# Other & Private
lm_h4b_intcov_other_private <- lm(
  formula   = morality_rating ~ partner_choice + transfer_ratio,
  data      = dplyr::filter(df_h4b, self_other == "other" & public_private == "private"),
  contrasts = list(partner_choice = "contr.sum"))
car::Anova(lm_h4b_intcov_other_private, type = 3)

# Other & Public
lm_h4b_intcov_other_public <- lm(
  formula   = morality_rating ~ partner_choice + transfer_ratio,
  data      = dplyr::filter(df_h4b, self_other == "other" & public_private == "public"),
  contrasts = list(partner_choice = "contr.sum"))
car::Anova(lm_h4b_intcov_other_public, type = 3)
```

------------------------------------------------------------------------

## X5: Exploratory Self/Other Analyses

```{r exploratory-5-prep-data, message=F, warning=F}
# --------- #
# PREP DATA #
# --------- #
df_x5 <- df_h4b |> 
  dplyr::mutate(
    transfer_ratio_meancentered = scale(transfer_ratio, scale = F), .after = transfer_ratio)
```

### Linear Model

```{r exploratory-5-lm, message=F, warning=F}
# ------------ # 
# LINEAR MODEL # 
# ------------ # 
lm_x5 <- lm(
  formula   = morality_rating ~ self_other * transfer_ratio_meancentered, 
  data      = df_x5,
  contrasts = list(self_other = "contr.sum"))

# -------------- # 
# TYPE III ANOVA #
# -------------- # 
anova_lm_x5 <- car::Anova(lm_x5, type = 3)
parameters::model_parameters(anova_lm_x5)
effectsize::effectsize(anova_lm_x5)

# ------------------------ #
# ESTIMATED MARGINAL MEANS #
# ------------------------ #
table(df_x5$self_other)
lm_x5_so_emm <- emmeans::emmeans(lm_x5, specs = ~self_other)
parameters::model_parameters(lm_x5_so_emm)

# -------------------- #
# PAIRWISE COMPARISONS #
# -------------------- #
parameters::model_parameters(
  emmeans::contrast(
    object = lm_x5_so_emm,
    method = "pairwise",
    infer  = T, 
    adjust = "none"))

# --------------------------------- #
# EFFECT SIZES FOR MEAN COMPARISONS #
# --------------------------------- #
parameters::model_parameters(
  emmeans::eff_size(
    object = lm_x5_so_emm, 
    sigma  = sigma(lm_x5), 
    edf    = df.residual(lm_x5)))

# ---------------------- #
# INTERACTION DECOMPOSED #
# ---------------------- #
lm_so_int_self <- lm(
  formula = morality_rating ~ transfer_ratio, 
  data    = df_x5 |> dplyr::filter(self_other == "self"))
parameters::model_parameters(lm_so_int_self)

lm_so_int_other <- lm(
  formula = morality_rating ~ transfer_ratio, 
  data    = df_x5 |> dplyr::filter(self_other == "other"))
parameters::model_parameters(lm_so_int_other)
```

### Curvilinear Model

```{r exploratory-5-qm, message=F, warning=F} 
# --------------- #
# QUADRATIC MODEL #
# --------------- #
qm_x5 <- lm(
  formula   = morality_rating ~ self_other * (transfer_ratio_meancentered + I(transfer_ratio_meancentered^2)), 
  data      = df_x5,
  contrasts = list(self_other = "contr.sum"))

# -------------- #
# TYPE III ANOVA #
# -------------- #
anova_qm_x5 <- car::Anova(qm_x5, type = 3)
parameters::model_parameters(anova_qm_x5)
effectsize::effectsize(anova_qm_x5)
```

## Model Comparison Statistics

```{r main-text-model-comparison-statistics, message=F, warning=F}
# ---------------- #
# MODEL COMPARISON #
# ---------------- #
dplyr::bind_rows(
  performance::compare_performance(lm_h2,  qm_h2),
  performance::compare_performance(lm_h3a, qm_h3a),
  performance::compare_performance(lm_h3b, qm_h3b),
  performance::compare_performance(lm_h4a, qm_h4a),
  performance::compare_performance(lm_h4b, qm_h4b),
  performance::compare_performance(lm_x5,  qm_x5)) |> 
  dplyr::mutate(
    Model = dplyr::if_else(
      stringr::str_starts(Name, 'lm'), 'Linear', 'Quadratic'))

# ---------------------- # 
# LIKELIHOOD RATIO TESTS #
# ---------------------- # 
lmtest::lrtest(lm_h2,  qm_h2)
lmtest::lrtest(lm_h3a, qm_h3a)
lmtest::lrtest(lm_h3b, qm_h3b)
lmtest::lrtest(lm_h4a, qm_h4a)
lmtest::lrtest(lm_h4b, qm_h4b)
lmtest::lrtest(lm_x5,  qm_x5)
```


```{r write-anonymized-data, message=F, warning=F}
# Write complete data to file
df_complete |> 
  dplyr::select(-c(
    matches("submit"), income, education, ses_1_x, ses_1_y, ses, 
    political_overall, political_overall_4_text, sexual_orientation,
    sexual_orientation_9_text, religiosity, region, believe_real_better,
    guess, technical, age, complete, comments_qs, sex, ethnicity_simplified,
    country_of_birth, country_of_residence, nationality, language, student_status,
    employment_status)) |> 
  vroom::vroom_write(
  here::here("pilot/data/clean/pilot-data-clean-complete-anonymized.csv"),
  delim = ",")
```

